### 2015-07-14 fundamentals/intro.tex
toward a solution to #116, I add more description of fleet-based on first mention. Additional description of fleet based and the challenges presented can be discussed.

The cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often fleet-based rather than
discrete and privately distributed rather than open source. These choices both
present challenges to modeling fidelity, generality, efficiency, robustness,
and scientific transparency.

>>>>

The cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are typically privately distributed
rather than open source and most acheive only fleet-level resolution of
facilities and materials rather than discrete resolution of those agents and
objects. Both choices present challenges to modeling fidelity, generality,
efficiency, robustness, and scientific transparency.
